Notebook of learning from ensemble labels

### 2021-07-18 docs/notebook_learn_dl_ensemble.Rmd
Update for new format

```
python hrlcm/fit_coteaching.py --exp_name unet_cot_gl_blind --lowest_score 9 --num_workers 32 --gpu_devices '0,1,2,3'
```

@@

```
python hrlcm/predict.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/model2_final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction2' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
```

@@

```
python hrlcm/evaluate.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/model1_final.pth' --data_dir 'results/north' --out_dir 'results/evaluation1' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
```

@@

- Deeplab3plus with ResNet as backbone. This architecture can consider the global context and have skip connections to ensure the complex structure still could get coverage.

### Possible strategies to deal with noisy labels

#### Add noisy labels to fine tune

@@

#### JoCoR
Since the original paper is about image classification rather than image segmentation, it is harder to adapt this method into image segmentation with good performance.

@@

>>>>

@@

@@

@@

### Possible strategies to deal with noisy labels
#### Add noisy labels to fine tune

@@

#### JoCoR

Since the original paper is about image classification rather than image segmentation, it is harder to adapt this method into image segmentation with good performance.

@@

So now, I have a clear idea is that the "wrong" guess labels are actually the hard ones. So instead of dumping them, we should take advantage of them.

- Randomly get 8 out of 64 for each tile, 6 for train, and 2 for validate.
- For these sub-tiles, score them and also correct the wrong part. The scores will be used as weight to calculate loss. The lower the score is, the higher weight it is.
